---
title: "Coding Assignment 3"
author: "Team 06"
date: "Due: 2022-12-09 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(gt)
library(gtsummary)
library(car) # for vif function
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r}
insurance <- read.csv("../Data/insurance_0126_Group6.csv")

gt(head(insurance))
```



## Question 1

Randomly select three observations from the sample and exclude from all modeling (i.e. n=47). Provide the summary statistics (min, max, std, mean, median) of the quantitative variables for the 47 observations.

```{r q1}
set.seed(123)

index <- sample(seq_len(nrow(insurance)), size = 3)

train <- insurance[-index,]
test <- insurance[index,]
summary(train)

train %>%
  tbl_summary(statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                      "{median} ({p25}, {p75})",
                                      "{min}, {max}"),
                all_categorical() ~ "{n} / {N} ({p}%)"),
type = all_continuous() ~ "continuous2")
```
According to the summary statistic output, the dependent variable, Charges is skewed to the right since it mean is higher than the median by about 2 thousand dollars. Since the standard deviation is high, some outliers could exist in the data.

## Question 2

Provide the correlation between all quantitative variables

```{r}
cor(insurance)
```
According to the correlation output,"Age" and "Smoker" variables are strongly and directly related to the dependent variable,Charges. Aditionally, no significant VIFs are found for independent variables and no concerning multicolllinearity is detected.

## Question 3

Run a regression that includes all independent variables in the data table. Does the model above violate any of the Gauss-Markov assumptions? If so, what are they and what is the solution for correcting?


```{r fig.height=8, fig.width=8}
original_model <- lm(Charges ~., data = train[,c(1:9)] ) #pulling only original data column before data transformation

summary(original_model)

par(mfrow=c(2,2))
plot(original_model)

vif(original_model)
```
The first plot


## Question 4

Implement the solutions from question 3, such as data transformation, along with any other changes you wish. Use the sample data and run a new regression. How have the fit measures changed? How have the signs and significance of the coefficients changed?

```{r q4}

#to detect non-linear realtionships and non-normally distributed variables
scatterplotMatrix(train[,c(1,2,3,5)])
```
Some nonlinearity between charges and Age have been found.

```{r q4}
#Data Transformation
#taking natural logirthm of Charges to bring possible outliers closer

par(mfrow=c(1,2))

hist(train$Charges) #before

train$lnCharges <- log(train$Charges)

hist(train$lnCharges) #after

```
Question#4 Answer==>
Taking natural logirthm of Charges transfrom the dependent variable to be more normally distributed.
 

```{r q4}
#Plotting the relationships After Transformation
scatterplotMatrix(train[,c(10,2,3)]) # grabbing lnCharges

#to determine if the relationship between Charges and Age is logarithmic or quadratic.

train$lnAge <- log(train$Age)
train$AgeSquared <- train$Age^2
scatterplotMatrix(train[,c(10,11,3)]) # lnChares & lnAge
scatterplotMatrix(train[,c(10,12,3)]) # lnChares & AgeSquared

```

Question#4 Answer==>

```{r fig.height=8, fig.width=8}
# New Regression
# Models to look at the regression coefficients.

# Model 1lnAge: Age with a logaritmic shape

model_1lnAge <- lm(lnCharges ~., data = train[,c(10,11,3:9)] )

summary(model_1lnAge)

# or

tbl_regression(model_lnAge,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(model_lnAge)$adj.r.squared* 100,digits = 2),"%")))
par(mfrow=c(2,2))
plot(model_lnAge)
```
Model1- LnAge Interpretation: the coefficent 


```{r fig.height=8, fig.width=8}
# Model 2AgeSq:Quadratic Relationship between Age and Charges

model_2AgeSq <- lm(lnCharges ~., data = train[,c(10,3:9,12)] )

summary(model_2AgeSq)

# or

tbl_regression(model_2AgeSq,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(model_2AgeSq)$adj.r.squared* 100,digits = 2),"%")))
par(mfrow=c(2,2))
plot(model_2AgeSq)

```


## Question 5

Use the 3 withheld observations and calculate the performance measures for your best two models. Which is the better model? (remember that "better" depends on whether your outlook is short or long run)

```{r q5}
test$lnCharges <- log(test$Charges)
test$lnAge <- log(test$Age)
test$AgeSquared <- test$Age^2

test$original_model_pred <- predict(original_model, newdata = test)

test$model_1lnAge_pred <- predict(model_1lnAge,newdata = test) %>% exp()

test$model_2AgeSq_pred <- predict(model_2AgeSq,newdata = test) %>% exp()

```

```{r q5}
# Finding the error

test$error_OM <- test$original_model_pred - test$Charges

test$error_1ln<- test$model_1lnAge_pred - test$Charges

test$error_2Sq<- test$model_2AgeSq_pred - test$Charges
# what does it do??? where to look for the output? **** Ask prof?
```


```{r q5}
# Bias

# Original Model
mean(test$error_OM)

# Model 1ln
mean(test$error_1ln)

# Model 2Sq
mean(test$error_2Sq)

```
BIAS
[1] 4879.738
[1] 2656.491 (best) over prediction
[1] 7168.83
```{r q5}
# MAE

mae <- function(error_vector){
  error_vector %>% 
  abs() %>% 
  mean()}

# Original Model
mae(test$error_OM)

# Model 1ln
mae(test$error_1ln)

# Model 2Sq
mae(test$error_2Sq)

```
MAE
[1] 5721.517
[1] 9328.276 take the abs value first
[1] 12033.55
```{r q5}
### RMSE
rmse <- function(error_vector){
   error_vector^2 %>% 
  mean() %>% 
  sqrt()}

# Original Model
rmse(test$error_OM)
# Model 1ln
rmse(test$error_1ln)

# Model 2Sq
rmse(test$error_2Sq)
```
RMSE
[1] 6627.591
[1] 11853.78 better
[1] 17117.81

```{r}
### MAPE
mape <- function(error_vector, actual_vector){
  (error_vector/actual_vector) %>% 
    abs() %>% 
    mean()
}

# Original Model
mape(test$error_OM, test$Charges)
# Model 1ln
mape(test$error_1ln, test$Charges)

# Model 2Sq
mape(test$error_2Sq, test$Charges)
```
# Question 5 Answer
Summary of Performance Metrics
BIAS
[1] 4879.738
[1] 2656.491 lower bias better for long run
[1] 7168.83
MAE
[1] 5721.517
[1] 9328.276 better
[1] 12033.55
RMSE (larger deviation) more accuracy short run
[1] 6627.591
[1] 11853.78 better more accurate in the short run
[1] 17117.81
MAPE
[1] 0.3584357
[1] 0.406728 better
[1] 0.4912408

is our intrest long run or short run?
which model is the best? =>lnage

tractor answer example=>Looking at these three models, the initial model was the worst performing (not surprising). Looking at the other two, the logarithmic relationship has lower bias, MAE, and MAPE. Model 2 has a lower RMSE meaning that there were not large prediction errors. Picking which model would depend on your time preference. If you are looking at the short-run, then Model 2. Model 1 if you are looking at the long-run.

## Question 6

Provide interpretations of the coefficients, do the signs make sense? Perform marginal change analysis (thing 2) on the independent variables.

```{r}
original_model$coefficients[2]*.25
```

## Question 7

An eager insurance representative comes back with five potential clients. Using the better of the two models selected above, provide the prediction intervals for the five potential clients using the information provided by the insurance rep.

| Customer | Age | BMI | Female | Children | Smoker | City           |
| -------- | --- | --- | ------ | -------- | ------ | -------------- | 
| 1        | 60  | 22  | 1      | 0        | 0      | Oviedo         |
| 2        | 40  | 30  | 0      | 1        | 0      | Sanford        |
| 3        | 25  | 25  | 0      | 0        | 1      | Winter Park    |
| 4        | 33  | 35  | 1      | 2        | 0      | Winter Springs |
| 5        | 45  | 27  | 1      | 3        | 0      | Oviedo         |


```{r}

```

## Question 8

The owner notices that some of the predictions are wider than others, explain why.

## Question 9 

Are there any prediction problems that occur with the five potential clients? If so, explain.

