---
title: "Coding Assignment 3"
author: "Team 06"
date: "Due: 2022-12-09 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(gt)
library(gtsummary)
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r}
insurance <- read.csv("../Data/insurance_0126_Group6.csv")
gt(head(insurance))
```



## Question 1

Randomly select three observations from the sample and exclude from all modeling (i.e. n=47). Provide the summary statistics (min, max, std, mean, median) of the quantitative variables for the 47 observations.

```{r q1}
set.seed(123)

index <- sample(seq_len(nrow(insurance)), size = 3)

train <- insurance[-index,]
test <- insurance[index,]
summary(train)

train %>%
  tbl_summary(statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                      "{median} ({p25}, {p75})",
                                      "{min}, {max}"),
                all_categorical() ~ "{n} / {N} ({p}%)"),
type = all_continuous() ~ "continuous2")
```


## Question 2

Provide the correlation between all quantitative variables

```{r}
cor(insurance)
```
Find the correlation between the variables - if closer to 1 that means it's positively correlated. Closer to -1 means negatively correlated.

## Question 3

Run a regression that includes all independent variables in the data table. Does the model above violate any of the Gauss-Markov assumptions? If so, what are they and what is the solution for correcting?
```{r fig.height=4, fig.width=4}
model <- lm(Charges ~. , data = train)

summary(model)

par(mfrow=c(2,2))
plot(model)
```
The first plot "Residuals vs. Fitted" displays a non-linear relationship, which violates the Gauss-Markov classical assumption.

"Normal Q-Q" displays the assumption of a normally distributed dependent variable for a fixed set of predictors. Without a better line of best fit, we can't verify this.

The "Scale-Location" and the "Residuals vs Leverage" models check for homoskedasticity. This assumption is violated due to the "fanning out" effect present on both models. If this assumption wasn't violated, random points would be present around a horizontal line.

## Question 4

Implement the solutions from question 3, such as data transformation, along with any other changes you wish. Use the sample data and run a new regression. How have the fit measures changed? How have the signs and significance of the coefficients changed?

```{r q4}
trainln <- log(train)

trainln <- do.call(data.frame, lapply(trainln, function(x) replace (x, is.infinite(x), 1)))

model <- lm(Charges ~. , data = trainln)

summary(model)

par(mfrow=c(2,2))
plot(model)
```
The fit measures have changed to be more correlated with the regression line though there are still outliers present. Where before the Gauss-Markov assumptions were being violated in the majority of the models, these updated models are now fitted along the regression line vs before.

``` {r}
cor(trainln)
```
How have the signs and significance of the coefficients changed?

Have to explain positive and negative correlations between coefficients such as age vs charges, smoker vs charges, etc.

## Question 5

Use the 3 withheld observations and calculate the performance measures for your best two models. Which is the better model? (remember that "better" depends on whether your outlook is short or long run)

```{r q4}

```


## Question 6

Provide interpretations of the coefficients, do the signs make sense? Perform marginal change analysis (thing 2) on the independent variables.

```{r}

```

## Question 7

An eager insurance representative comes back with five potential clients. Using the better of the two models selected above, provide the prediction intervals for the five potential clients using the information provided by the insurance rep.

| Customer | Age | BMI | Female | Children | Smoker | City           |
| -------- | --- | --- | ------ | -------- | ------ | -------------- | 
| 1        | 60  | 22  | 1      | 0        | 0      | Oviedo         |
| 2        | 40  | 30  | 0      | 1        | 0      | Sanford        |
| 3        | 25  | 25  | 0      | 0        | 1      | Winter Park    |
| 4        | 33  | 35  | 1      | 2        | 0      | Winter Springs |
| 5        | 45  | 27  | 1      | 3        | 0      | Oviedo         |


```{r}

```

## Question 8

The owner notices that some of the predictions are wider than others, explain why.

## Question 9 

Are there any prediction problems that occur with the five potential clients? If so, explain.

