---
title: "Coding Assignment 1"
author: "Team 6"
date: "Due: 2022-09-25 23:59"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(readxl)
library(gtsummary)
library(tidyverse)
library(plotly)
library(gt)
library(corrplot)
```


A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


**For this assignment, ignore the categorical variables (gender, smoker, cities)**

```{r}
insurance_0126_Group6 <- read_excel("Data/insurance_0126_Group6.xlsx")
insurance1 <- subset(insurance_0126_Group6, select = c("Charges","Age","BMI","Children"))
```

# Question 1

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

```{r q1}
# CENTER 
summary(insurance1)

#MODE
getModes <- function(x) {
ux <- unique(x)
tab <- tabulate(match(x, ux))
ux[tab == max(tab)]
}
getModes(insurance1$Charges)
getModes(insurance1$Age)
getModes(insurance1$BMI)
getModes(insurance1$Children)

#SHAPE
hist(insurance1$Charges)
hist(insurance1$Age)
hist(insurance1$BMI)
hist(insurance1$Children)

#BOXPLOT
boxplot(insurance1$Charges,
  ylab = "Charges")
main = "Boxplot of Charges"
boxplot.stats(insurance1$Charges)$out
out <- boxplot.stats(insurance1$Charges)$out
mtext(paste("Outliers: ", paste(out, collapse = ", ")))

boxplot(insurance1$Charges,
  ylab = "Age")
main = "Boxplot of Age"
boxplot.stats(insurance1$Age)$out
out <- boxplot.stats(insurance1$Age)$out
mtext(paste("Outliers: ", paste(out, collapse = ", ")))

boxplot(insurance1$Charges,
  ylab = "BMI")
main = "Boxplot of BMI"
boxplot.stats(insurance1$BMI)$out
out <- boxplot.stats(insurance1$BMI)$out
mtext(paste("Outliers: ", paste(out, collapse = ", ")))

boxplot(insurance1$Charges,
  ylab = "Children")
main = "Boxplot of Children"
boxplot.stats(insurance1$Children)$out
out <- boxplot.stats(insurance1$Children)$out
mtext(paste("Outliers: ", paste(out, collapse = ", ")))

#SPREAD 
##Charges
var(insurance1$Charges, na.rm = TRUE)
sd(insurance1$Charges, na.rm = TRUE)
IQR(insurance1$Charges, na.rm = TRUE)
range(insurance1$Charges, na.rm = TRUE)

##Age
var(insurance1$Age, na.rm = TRUE)
sd(insurance1$Age, na.rm = TRUE)
IQR(insurance1$Age, na.rm = TRUE)
range(insurance1$Age, na.rm = TRUE)

##BMI
var(insurance1$BMI, na.rm = TRUE)
sd(insurance1$BMI, na.rm = TRUE)
IQR(insurance1$BMI, na.rm = TRUE)
range(insurance1$BMI, na.rm = TRUE)

##Children
var(insurance1$Children, na.rm = TRUE)
sd(insurance1$Children, na.rm = TRUE)
IQR(insurance1$Children, na.rm = TRUE)
range(insurance1$Children, na.rm = TRUE)
```
Interpretation Question #1:CHARGES
Upon observing the R-Studio outputs of the dataset, the distribution of the “Charges” is positively skewed to the right since “Mean” value is greater than “Median” value.ie: mean $10623 > median $8169.
There is no mode for the “Charges” and 5 outliers are detected from box plot and. The std deviation of “Charges” is affected by those outliers and the value being larger than the “Mean”, the best measure for the central tendency of Charges is median value $8169.
AGE
It is observed the mean and median values of “Age” are respectively 39.42 and 37.5 and thus data set has nearly symmetrical distribution. One mode value of “26” is detected and the distribution is unimodal. Also, with the IQR value of 27, no outliers were detected, and the fact is reflected by the low Standard Deviation value of 15.39. With low Standard Deviation value and nearly the same value of mean and median, the best the measure for the central tendency of Age is mean value of 39.42.
BMI
For BMI dataset, the “Mean” and “Median” value are nearly identical with the value of 30.59 and 30.73 and thus the distribution is found to be symmetrical. No outliers were detected, and thus Standard deviation value is small with the value of 6.142993. With 2 mode values of 30.59 and 32.965 the distribution is Bimodal. For a bimodal distribution, the best measure to capture the central tendency of o BMI data is the mode and the value should be 32.965.
CHILDREN
For Children data set, the Mean value of 1.0 is greater than the Median Value of 0.5 and thus the distribution is positively skewed. The distribution is unimodal with the mode value of “0”. No outliers are detected and Standard deviation is small with 1.22 and thus the best measure for central tendency is the mean and the value is 1.0

# Question 2

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 

```{r q2,echo=FALSE, warning=FALSE}

cor(insurance1$Charges,insurance1$Age)

plot(insurance1$Charges,insurance1$Age)

abline(lm(Age ~ Charges, data = insurance1),lty = 1)

cor(insurance1$Charges,insurance1$BMI)

plot(insurance1$Charges,insurance1$BMI)

abline(lm(BMI ~ Charges, data = insurance1),lty = 1)

cor(insurance1$Charges,insurance1$Children)

plot(insurance1$Charges,insurance1$Children)

abline(lm(Children ~ Charges, data = insurance1),lty = 1)

```
Interpretation for Question #2:

There is a strong, positive, linear association between the age of the patient and the total medical expenses for their insurance plans, meaning that as patients get older, it is more expensive for them to pay for their insurance plan.

There is a weak, positive, linear association between the patient's body mass index and the total medical expenses for their insurance plan. This means that as the body mass index of the patient rises, the expenses of their insurance plan also rises. This means that it is more expensive to pay for their insurance as their health gets worse (since BMI is normally used as a measurement of someone's weight vs their age in relation to overall health).

There is a moderately strong, negative, linear association between the number of children or other dependents covered by an insurance plan and the total medical expenses for their insurance plan. This means that as additional dependents or children get added to a plan, the less the plan costs overall.

# Question 3

Generate a regression equation in the following form:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$$

```{r q3}
model <- lm(Charges ~ Age + BMI + Children, data = insurance1)
summary(model)
```

also write out the regression cleanly in this document.

Charges = -# + # * Age + # * BMI - # * Children 

From this linear function, we can then hypothesize the signs of the coefficients:

- $\beta_{Age}$ < 0: We would expect the number of charges to increase as the age of beneficiaries is higher   (holding BMI and birth sex constant)
- $\beta_{BMI}$ > 0: We would expect the number of charges to increase as the number of BMI increases
- $\beta_{Children}$ weakly positive?: We might expect as there are more children covered by health insurance, number of charges would decrease as one can predict that children are healthier that older population

# Question 4

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)


```{r q4}
newPrediction <- data.frame(Age = 40,
                            BMI = 30,
                            Children = 1)
predict(model, newdata = newPrediction, interval = "confidence", level = .95)
```