---
title: "Coding Assignment 2"
author: "Team 6"
date: "Due: 2021-10-23 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(jtools)
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0126_Group6.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$

```{r q1}
model <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = insurance)
regsummary <- summary(model)
regsummary
```

Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$

Based on the results above, we can see that BMI and WinterSprings are the only independent variables that tested significant at the 80% level. This means that we have sufficient evidence in that the slopes of the coefficients are different than zero.

There is insufficient evidence to conclude that the slope coefficient of Oviedo is different than zero in a two tailed test. 

However, Oviedo would have tested significant on a one-tailed test. We can justify a one tailed test because Oviedo and WinterSprings are two well-established sister cities located in Seminole County, just northeast of Orlando.

## Question 2

Interpret the coefficients of all the independent variables that tested significant.

BMI SEE = 95.01
C.V at 80%, two tail test = 1.2816
MOE = 95.01 * 1.2816 = 121.76

If a client's BMI increases by 1, charges are expected to increase by 141 points, give or take 122 points. 


WinterSprings SEE = 1632.11
C.V at 80%, two tail test = 1.2816
MOE = 1632.11 * 1.2816 = 2091.712

If a client lives in WinterSprings, he/she is expected to pay higher premium of $3,263 give or take 2,092 points.


## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3}
newPredictiondummy <- data.frame(Age =35 ,
                            BMI = 26,
                            Children = 1,
                            Female=1,
                            Smoker=0,
                            WinterSprings=0,
                            WinterPark=0,
                            Oviedo=0)
predict(model, newdata= newPredictiondummy, interval = "confidence",levels=.95)


```

The predicted amount of medical expenses associated with a policy for a client with the above stated characteristic is $4,630.

## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}
reduced_insurance <- insurance[,-(7:9)]

model_reduced <- lm(Charges ~. , data = reduced_insurance)

summary(model_reduced)
```
```{r q4.1}
anova(model_reduced, model )
```
```{r q4.2}
insurance_dummy <- insurance[,-(7:9)]

insurance_model <- lm(Charges ~. , data = insurance_dummy)

summary(insurance_model)
```
By using the partial F-test to compare Question 1's 41 degrees of freedom vs Question 4's 44 degrees of freedom, we are able to determine that including both does indicate that by using 0.05 the SSE was reduced by a statistically significant amount but that neither was statistically significant if tested independently.

This means that though some factors like age (or other displayed factors) will affect insurance premiums, cities themselves won't affect the premiums much in comparison.
